% TASNI Paper - Abstract
% Thermal Anomaly Search for Non-communicating Intelligence

\begin{abstract}

We present the Thermal Anomaly Search for Non-communicating Intelligence (TASNI), a systematic pipeline to identify mid-infrared sources in the AllWISE catalog that lack counterparts at optical, near-infrared, and radio wavelengths. From 747 million AllWISE sources, our multi-wavelength veto strategy isolates 4,137 ``thermal anomalies''---objects detectable only in the mid-infrared with thermal colors (W1$-$W2 $> 0.5$~mag). The 100 highest-scoring candidates (``golden sample'') have mean effective temperature $T_{\rm eff} = 265 \pm 36$~K, mean W1$-$W2 color of $1.99 \pm 0.36$~mag, and mean proper motion $\mu = 216 \pm 149$~mas~yr$^{-1}$, consistent with extremely cold brown dwarfs at distances of 20--100~pc. Analysis of 10-year NEOWISE light curves reveals that 45\% of the golden sample is photometrically stable, 50\% shows variability consistent with brown dwarf atmospheres, and 5\% exhibits systematic fading. We identify four ``fading thermal orphans''---sources with unprecedented combinations of extreme W1$-$W2 colors (1.53--3.37~mag), room-temperature emission ($T_{\rm eff} = 251$--293~K), high proper motions (55--359~mas~yr$^{-1}$), and monotonic fading at rates of 18--53~mmag~yr$^{-1}$ over the decade-long baseline. None of these four sources appear in SIMBAD or any astronomical catalog. The most likely interpretation is that these objects are extremely cold Y-type brown dwarfs, possibly young objects undergoing rapid cooling. While our search was partly motivated by the technosignature hypothesis, all observed properties are consistent with natural astrophysical sources. Spectroscopic follow-up is urgently needed to confirm the nature of these unusual objects and determine whether they represent the coldest brown dwarfs yet identified or an entirely new class of astronomical sources.

\end{abstract}

% Keywords
\keywords{brown dwarfs --- infrared: stars --- stars: low-mass --- surveys --- techniques: photometric}
